---
title: "Complexity Reduction"
---

In this notebook, I will try to write a script that does a complexity-reduction for the samples that are in the same disease state. As we were unable to get phenotypic and/or more detailed diagnosis (e.g. which stage of cancer, other secondary diagnoses), I am interested in seeing the degree of difference within. 
From what I have read, PCA is a linear complexity reduction algorithm, but I don't think gene expressions are linear, so will try t-SNE instead.

```{r}
library('Rtsne')
directory <- "../data/processed_raw_counts.tsv"
data <- read.table(directory, sep='\t', header=TRUE, row.names=1)
```

```{r}
N <- nrow(data)
sdata <- data[1:(N-40000),]
h <- sdata[,grepl("H",names(data))]
s <- sdata[,grepl("S",names(data))]
n <- sdata[,grepl("N",names(data))]
c <- sdata[,grepl("C",names(data))]
```

```{r}
set.seed(13)
tsne_h <- Rtsne(as.matrix(unique(t(h))))#, theta=0.20)

th <- ggplot(data.frame(tsne_h$Y), aes(X1, X2)) + 
      geom_point(alpha=0.55, size=1.25) +
      ggtitle ("Healthy")
# ggsave("../pictures/tSNE_healthy.png", plot=last_plot(), scale=1.5,
#         dpi=450, width=5, height=3)

th
```

```{r}
pca_h <- prcomp(h, scale.=T, center=TRUE)
plot(pca_h)
summary(pca_h)
```