---
title: "DESeq Analysis"
output: DESeq_Analysis
---

First, the data needs to be loaded (obviously).

```{r}
directory <- "../data/processed_raw_counts.tsv"
data <- read.table(directory, sep='\t', header=TRUE, row.names=1)
N <- nrow(data)
data <- data[1:(N-45000),]
```

Second, we need to collect all the column names/header to classify our samples: H(ealthy), S(teatosis), N(on-alcoholic steatohepatitis), and C (Hepatocellular carcinoma). Preparing for processing by loading the DESeq library.

```{r} 
healthy <- data[,grepl("H",names(data))]
steatosis <- data[,grepl("S",names(data))]
nash <- data[,grepl("N",names(data))]
cancer <- data[,grepl("C",names(data))]
source("http://www.bioconductor.org/biocLite.R")
library("DESeq2")
```

Third, we need to prepare the data by appropriating the input format for DESeq2.

```{r}
total_data <- cbind(healthy, steatosis, nash, cancer)
total_data <- round(total_data,0)
col_names <- colnames(total_data)
condition <- c(rep("H", length(healthy)), rep("S", length(steatosis)), rep("N", length(nash)), rep("C", length(cancer)))
(coldata <- data.frame(row.names=colnames(total_data), condition))
```

Now we begin...

```{r}
dds <- DESeqDataSetFromMatrix(countData=total_data, colData=coldata, design=~condition)
dds <- DESeq(dds)
```

Finally, we print some of the results... (and also saving the output into our results directory)
```{r}
HS <- data.frame(results(dds, contrast = c('condition', "H", "S")))
SN <- data.frame(results(dds, contrast = c('condition', "S", "N")))
SC <- data.frame(results(dds, contrast = c('condition', "N", "C")))
```
