---
title: "DESeq"
output: DESeq
---

Similarly, also testing this on DESeq. As before, the processed raw counts are loaded.

```{r}
directory <- "../data/processed_raw_counts.tsv"
data <- read.table(directory, sep='\t', header=TRUE, row.names=1)
N <- nrow(data)
data <- data[1:(N-45000),]
```

Second, we need to collect all the column names/header to classify our samples: H(ealthy), S(teatosis), N(on-alcoholic steatohepatitis), and C (Hepatocellular carcinoma). Preparing for processing by loading the DESeq library.

```{r}
healthy <- data[,grepl("H",names(data))]
steatosis <- data[,grepl("S",names(data))]
nash <- data[,grepl("N",names(data))]
cancer <- data[,grepl("C",names(data))]
source("http://www.bioconductor.org/biocLite.R")
library("DESeq")
```

Third, we need to prepare the data by appropriating the input format for DESeq.

```{r}
total_data <- cbind(healthy, steatosis, nash, cancer)
total_data <- round(total_data,0)
col_names <- colnames(total_data)
condition <- c(rep("H", length(healthy)), rep("S", length(steatosis)), rep("N", length(nash)), rep("C", length(cancer)))
#coldata <- data.frame(row.names=colnames(total_data), condition)
```

Now we begin:

```{r}
cds <- newCountDataSet(total_data, condition)
cds <- estimateSizeFactors(cds)
cds <- estimateDispersions(cds)
res_HS <- nbinomTest(cds, "H", "S")
res_SN <- nbinomTest(cds, "S", "N")
res_NC <- nbinomTest(cds, "N", "C")

```



